---
title: "Summary Reports V3"
author: "FdR"
date: "2/13/2022"
output: html_document
---

This reports are there to help me make better trading decisions. 

# TODO: 

* more for sectors ... check percentage above 50SMA or 43EMA and consequent on return for next 31 days, and 43 days
a graph with volume ... how is the EMA9 volume comparing to the rolling 252 days average volume


# Thoughts 

* I have put lots of emphasis on precision (50% on precision and 20% on soft-precision).  Because it is so hard to get it exactly right and because we have so many models that are prediction first a "3" but then a "1" which then is so confusing to deal with ... Maybe it is better to put more emphasis on soft-precision instead of pure precision.  

```{r setup, include=FALSE}
library(knitr)

knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
the_path <- here::here()

source('../functions/summary_reports_v3.R')
source('../functions/chart_plotting_v1.R')
source('../functions/fmpr_functions.R')
```

# Download data EoD data and create charts 

This is just to download data for which I have a model 
```{r download_data_1}
etf_tickers <- c("XLF", "XLI", "XLY", "XLV", "XME", "XLB", "XBI", "IYT", "HACK", "VOX", "ITB", "FXG", 
                 'VCR', 'XLC', 'IYW', 'VGT', 
                 "SMH", "IPAY", "SPY", "RSP", "QQQ", "XLE", "VDE", "XOP", "GDXJ", "VAW", 
                 'PBW', "EEM", 'DIA', 'GDX', 
                 "KWEB", "HYG", "TLT", "DBB", "DBA", "IWD", "IWF")

for (i in 1:length(etf_tickers)) { 
  tryCatch({ 
    get_fmpr_prices(etf_tickers[i])
    print(glue("just downloaded data for ", etf_tickers[i], " and saved it."))
    }, error=function(e){cat("ERROR :",conditionMessage(e), "\n")})
}


stock_tickers <- c("AMD", "TSM", "BAH", "PYPL", "JPM", "AXP", 
                   "TFII", "FDX", "CAT", "HAL", "CVX", "PSX", 
                   "BBWI", "SBUX", "MNST", "DIS", "PARA", 
                   "GILD", "CGC", 
                   "PAAS", "AA", "VALE", "STLD", "MOS", 
                   "ATKR", "RYN", 'NVDA')

for (i in 1:length(stock_tickers)) { 
  tryCatch({ 
    get_fmpr_prices(stock_tickers[i])
    print(glue("just downloaded data for ", stock_tickers[i], " and saved it."))
    }, error=function(e){cat("ERROR :",conditionMessage(e), "\n")})
}
```


```{r plot_data}
df <- tibble(ticker = etf_tickers) 
pdf(paste0(the_path,"/charts/charts_markets.pdf"), width=13, height=8, onefile = TRUE)
for (i in 1:nrow(df)){ 
  print(df$ticker[i])
  yo <- tibble(ticker = df$ticker[i]) %>% 
    mutate(raw_df = map(ticker, function(.x) conform_data(.x, "Daily", "fmpr")), 
           ext_df = map(raw_df, create_plot_fin_df))
  create_candlestick_chart(yo$ext_df[[1]], yo$ticker, start_date = today()-600, end_date = today())
  create_vol_candlestick_chart(yo$ext_df[[1]], yo$ticker, start_date = today()-600, end_date = today())
  Sys.sleep(2)
  }
dev.off()
```


Creating charts for tickers. They are available for review as pdf in the portfolio folder. 

```{r plot_data2}
tickers = c("AMD", "TSM", "BAH", "PYPL", "AXP", "JPM", 
            "GILD", "BBWI", "SBUX", "MNST", "DIS", "PARA",
            "FDX", "CAT", "AA", "CVX", "HAL", "MOS", "STLD", "PAAS") 

etf1 = c("QQQ", "QQQ", "SPY", "QQQ", "SPY", "SPY", 
         "SPY", "SPY", "SPY", "SPY", "SPY", "SPY", 
         "SPY", "SPY", "SPY", "SPY", "SPY", "SPY", "SPY", "DIA")

etf2 = c("SMH", "SMH", "HACK", "IPAY", "XLF", "XLF", 
         "XLV", "XLY", "XLY", "FXG", "VOX", "VOX", 
         "IYT", "XLI", "XME", "XLE", "VDE", "VAW", "VAW", "GDX")

df <- tibble(ticker = tickers, etf1 = etf1, etf2 = etf2) 
pdf(paste0(the_path,"/charts/charts_stocks.pdf"), width=13, height=8, onefile = TRUE)
for (i in 1:nrow(df)){ 
  print(df$ticker[i])
  yo <- tibble(ticker = tickers[i], etf1 = etf1[i], etf2 = etf2[i]) %>% 
    mutate(raw_df = map(ticker, function(.x) conform_data(.x, "Daily", "fmpr")), 
           ext_df = map(raw_df, create_plot_fin_df))
  create_candlestick_chart(yo$ext_df[[1]], yo$ticker, 
                           start_date = today() - 365, 
                           end_date = today())
  create_vol_candlestick_chart(yo$ext_df[[1]], 
                               yo$ticker, 
                               start_date = today() - 365, 
                               end_date = today())
  create_rel_candlestick_chart(df$ticker[i], 
                               df$etf1[i], 
                               df$etf2[i], 
                               df$ticker[i], 
                               start_date = today() - 365, 
                               end_date = today())  
  Sys.sleep(2)
  }
dev.off()
```

```{r plot_data3}
tickers <- c("ABNB", "GOOG", 'META', "AAPL", "NFLX", 
             'SQ', 'PYPL', 'TSLA', 'TWLO', 
             'AMZN', 'CGC', 'BMY', 'LLY', 'BA')
etf1 <- c('QQQ', 'QQQ', 'QQQ', 'SPY', 'QQQ', 
          'QQQ', 'QQQ',  'QQQ', 'QQQ', 
          'QQQ', 'SPY', 'SPY', 'SPY', 'SPY')
etf2 <- c('VCR', 'VOX', 'XLC',  'IYW', 'XLC', 
          'IPAY', 'IPAY', 'VCR', 'VGT', 
          'XLY', 'XLV', 'XLV', 'XLV', 'XLI')

for (i in 1:length(tickers)) { 
  tryCatch({ 
    get_fmpr_prices(tickers[i])
    print(glue("just downloaded data for ", tickers[i], " and saved it."))
    }, error=function(e){cat("ERROR :",conditionMessage(e), "\n")})
}

df <- tibble(ticker = tickers, etf1 = etf1, etf2 = etf2) 
pdf(paste0(the_path,"/charts/charts_tech.pdf"), width=13, height=8, onefile = TRUE)
for (i in 1:nrow(df)){ 
  print(df$ticker[i])
  yo <- tibble(ticker = tickers[i], etf1 = etf1[i], etf2 = etf2[i]) %>% 
    mutate(raw_df = map(ticker, function(.x) conform_data(.x, "Daily", "fmpr")), 
           ext_df = map(raw_df, create_plot_fin_df))
  create_candlestick_chart(yo$ext_df[[1]], yo$ticker, 
                           start_date = today() - 365, 
                           end_date = today())
  create_vol_candlestick_chart(yo$ext_df[[1]], 
                               yo$ticker, 
                               start_date = today() - 365, 
                               end_date = today())
  create_rel_candlestick_chart(df$ticker[i], 
                               df$etf1[i], 
                               df$etf2[i], 
                               df$ticker[i], 
                               start_date = today() - 365, 
                               end_date = today())  
  Sys.sleep(2)
  }
dev.off()
```

```{r portfolio}
st <- c('EWH', 'GDXJ', 'CGC', 'EEM', 'EWJ', 'CBOE', 'NEE')

for (i in 1:length(st)) { 
  tryCatch({ 
    get_fmpr_prices(st[i])
    }, error=function(e){cat("ERROR :",conditionMessage(e), "\n")})
}
df <- tibble(ticker = st) 
pdf(paste0(the_path,"/charts/charts_portf.pdf"), width=13, height=8, onefile = TRUE)
for (i in 1:nrow(df)){ 
  print(df$ticker[i])
  yo <- tibble(ticker = df$ticker[i]) %>% 
    mutate(raw_df = map(ticker, function(.x) conform_data(.x, "Daily", "fmpr")), 
           ext_df = map(raw_df, create_plot_fin_df))
  create_candlestick_chart(yo$ext_df[[1]], yo$ticker, start_date = today()-350, end_date = today())
  create_vol_candlestick_chart(yo$ext_df[[1]], yo$ticker, start_date = today()-350, end_date = today())
  Sys.sleep(2)
  }
dev.off()
```

```{r}
#downloading foreign markets
st <- c('EWQ', 'EWP', 'EWG', 'EPOL', 'EEM', 'EWZ', 'EWW', 'EWJ', 'EWY', 'EWS', 'EWM', 'THD', 'EIDO', 'EPHE', 'EWA', 'EZA', 'EWC')
for (i in 1:length(st)) { 
  tryCatch({ 
    get_fmpr_prices(st[i])
    }, error=function(e){cat("ERROR :",conditionMessage(e), "\n")})
}
df <- tibble(ticker = st) 
pdf(paste0(the_path,"/charts/charts_foreign.pdf"), width=13, height=8, onefile = TRUE)
for (i in 1:nrow(df)){ 
  print(df$ticker[i])
  yo <- tibble(ticker = df$ticker[i]) %>% 
    mutate(raw_df = map(ticker, function(.x) conform_data(.x, "Daily", "fmpr")), 
           ext_df = map(raw_df, create_plot_fin_df))
  create_candlestick_chart(yo$ext_df[[1]], yo$ticker, start_date = today()-350, end_date = today())
  create_vol_candlestick_chart(yo$ext_df[[1]], yo$ticker, start_date = today()-350, end_date = today())
  Sys.sleep(2)
  }
dev.off()
```

ETF with highest monthly returns. 

```{r etf_returns}
return_ndays <- function(df, ndays = 21) { 
  yo <- df %>% mutate(returns = log(adjusted / lag(adjusted, n = ndays))) %>% 
    select(index, returns) %>% 
    filter(index > today() - 4)
  return(yo)
}

etf_returns_2 <- tibble(ticker = etf_tickers) %>% 
  mutate(raw_df = map(ticker, function(.x) conform_data(.x, "Daily", "fmpr")), 
         return_4w = map(raw_df, function(.x) return_ndays(.x))) %>% 
  select(-raw_df) %>% 
  unnest(cols = c("return_4w")) %>% arrange(returns)

```


# What is the recent historical volatility 

```{r historical_volatility}

library(roll)
ticker =  c("FDX", 'JPM', "AXP", "GILD", "SBUX","BBWI","PARA", "MOS", "AA", "CVX", "PYPL", "AMD", "CAT", "HAL")
volat <- tibble(ticker = NA, index = NA, adjusted = NA, ret_5w = NA, mean_ret_5w = NA, sd_ret_5w = NA, ret_7w = NA, 
                mean_ret_7w = NA, sd_ret_7w = NA,)
for (i in 1: length(ticker)) { 
  yo <- conform_data(ticker[i], "Daily", "fmpr") %>% arrange(index) %>% 
    mutate(ret_5w = round((adjusted / lag(adjusted, n = 26)) - 1, 3), 
           mean_ret_5w = round(roll_mean(ret_5w, width = 147), 3), 
           sd_ret_5w = round(roll_sd(ret_5w, width = 147), 3), 
           ret_7w = round((adjusted / lag(adjusted, n = 37)) - 1, 3), 
           mean_ret_7w = round(roll_mean(ret_7w, width = 147), 3), 
           sd_ret_7w = round(roll_sd(ret_7w, width = 147), 3), 
           ticker = ticker[i]) %>% 
           select(index, ticker, adjusted, ret_5w, mean_ret_5w, sd_ret_5w, ret_7w, mean_ret_7w, sd_ret_7w)
  volat <- bind_rows(volat, yo)
}

volat <- volat %>% arrange(desc(index), desc(sd_ret_5w))

```



# Evaluates models 

```{r} 
the_path <- here::here()
library(tidymodels)
library(embed)

tickers = c("FDX", 'JPM', "AXP", "GILD","SBUX","BBWI","PARA", "MOS", "AA", "CVX", "PYPL", "AMD", "CAT", "HAL")
etf1 = c(   "SPY", 'SPY', "SPY", "SPY", "SPY", "SPY", "SPY",  "SPY", "SPY","SPY", "QQQ",  "QQQ", "SPY", "SPY")
etf2 = c(   "IYT", 'XLF', "XLF", "XLV", "XLY", "XLY", "VOX",  'VAW', "XME","XLE", "IPAY", "SMH", "XLI", "VDE")

yo <- unique(etf2)
#yo <- c("XME","XLE", "IPAY", "SMH", "XLI", "VDE")
poss_get_profile = possibly(.f = get_fmpr_profile, otherwise = NA)

for (i in 1:length(yo)) { 
  df1 <- get_fmpr_etf_holder(yo[i]) |> 
    select(-updated, -marketValue, -weightPercentage) |> 
    filter(str_length(asset) <= 4) |> 
    mutate(profile = map(asset, poss_get_profile))  
  df2 <- df1 |>  
    unnest_wider(col = contains("profile")) |> 
    select(-symbol) |> 
    arrange(industry, mktCap) 
  write_csv(df2, paste0("etf/", yo[i], "_", today(), ".csv")) 
  for (j in 1:nrow(df1)) { 
    get_fmpr_prices(df1$asset[j]) 
    print(glue("Downloaded ticker ", df1$asset[j], " for etf ", yo[i])) 
    }
} 

```


```{r predictions, echo=FALSE, warning=FALSE, message=FALSE}

predictions = tibble(index=NA, ret_5w=NA, ord_class=NA, predictions=NA, 
                     pred_class=NA, ticker = NA, model=NA)

for (i in 1:length(tickers)) { 
  tryCatch({ 
    v6l <- predict_v6_long(tickers[i], tickers[i], etf1[i], etf2[i])
    predictions <- bind_rows(predictions, v6l)
    print(glue("Just created predictions for ", tickers[i], " using model V6.2 Long")) 
    }, error=function(e){cat("ERROR :",conditionMessage(e), "\n")})
  
  #tryCatch({ 
   # v6s <- predict_v6_short(tickers[i], tickers[i], etf1[i], etf2[i])
  #  predictions <- bind_rows(predictions, v6s)
   # print(glue("Just created predictions for ", tickers[i], " using model V6.2 Short"))
  #}, error=function(e){cat("ERROR :",conditionMessage(e), "\n")})
  
  tryCatch({   
    v7l <- predict_v7_long(tickers[i], tickers[i], etf1[i], etf2[i])
    predictions <- bind_rows(predictions, v7l)
    print(glue("Just created predictions for ", tickers[i], " using model V7.1 Long with ETF1 = ", 
               etf1[i], " and ETF2 = ", etf2[i]))
    }, error=function(e){cat("ERROR :",conditionMessage(e), "\n")})
  
    tryCatch({   
    v8l <- predict_v8_long(tickers[i], tickers[i], etf1[i], etf2[i])
    predictions <- bind_rows(predictions, v8l)
    print(glue("Just created predictions for ", tickers[i], " using model V8.1 Long with ETF1 = ", 
               etf1[i], " and ETF2 = ", etf2[i]))
    }, error=function(e){cat("ERROR :",conditionMessage(e), "\n")})
}

yo2 <- predictions %>% #filter(Index >= today() -5) %>% 
  mutate(date = today()) #%>% arrange(ticker, desc(Index))

yo3 <- yo2 %>% unnest(cols = c(predictions, pred_class)) %>% 
  mutate(ordered_pred = if_else(.pred_3 > .pred_2 & .pred_2 > .pred_1, 3, 
                                if_else(.pred_1 > .pred_2 & .pred_2 > .pred_3, 1, 0))) %>% 
  filter(index >= today() - 50) %>% select(-ord_class) %>% 
  arrange(desc(index), ticker)
yo <- yo2 %>% unnest(cols = c(predictions, pred_class))
write_csv(yo, paste0(the_path, "/portfolio/predictions/predictions_", today(), ".csv"))
#rm(v2l, v6l, v6s, v7l, yo2)

yo4 <- yo3 %>% 
  mutate(top_pred = if_else(.pred_1 > .pred_2 & .pred_1 > .pred_3, 1,
                        if_else(.pred_3 > .pred_1 & .pred_3 > .pred_2, 3, 2)), 
         mid_pred = case_when(.pred_1 > .pred_2 & .pred_1 < .pred_3 ~ 1, 
                              .pred_1 < .pred_2 & .pred_1 > .pred_3 ~ 1, 
                              .pred_2 < .pred_3 & .pred_2 > .pred_1 ~ 2, 
                              .pred_2 > .pred_3 & .pred_2 < .pred_1 ~ 2, 
                              TRUE ~ 3), 
         bottom_pred = if_else(.pred_1 < .pred_2 & .pred_1 < .pred_3, 1, 
                               if_else(.pred_3 < .pred_1 & .pred_3 < .pred_2, 3, 2)))
yo5 <- yo4 %>% 
  group_by(ticker, index) %>% 
  summarise(top_pred = mean(top_pred), 
            mid_pred = mean(mid_pred), 
            bot_pred = mean(bottom_pred)) %>% 
  mutate(top_2 = (top_pred + mid_pred)/2, 
         bottom_2 = (mid_pred + bot_pred)/2) %>% 
  arrange(desc(index), desc(top_pred), desc(mid_pred))

```

What stocks have had improved and deterioriating scores? 
```{r eval=FALSE}
yo <- yo5 %>% select(ticker, index, top_pred, mid_pred, bot_pred) %>% 
  arrange(index) %>% 
  group_by(ticker) %>% 
  mutate(ordered_top = if_else(top_pred > mid_pred & mid_pred > bot_pred, 3, 
                               if_else(bot_pred > mid_pred & mid_pred > top_pred, 1, 0)), 
         changed_top_pred = if_else(top_pred > lag(top_pred), 1, 
                                    if_else(top_pred < lag(top_pred), -1, 0)), 
         changed_bot_pred = if_else(bot_pred > lag(bot_pred), -1, 
                                    if_else(bot_pred < lag(bot_pred), 1, 0))) %>% 
  ungroup() %>% 
  filter(changed_top_pred == 1 | changed_top_pred == -1 | changed_bot_pred == 1 | changed_bot_pred == -1) %>% 
  group_by(ticker) %>% 
  arrange(desc(index)) %>% 
  slice_head(n = 5) %>% 
  ungroup() %>% 
  arrange(ticker, desc(index))

```


```{r}
library(dplyr)
library(readr)
library(lubridate)
library(ggplot2)
library(gridExtra)
library(bdscale)

the_path <- here::here()

test_files <- list.files(path = paste0(the_path, '/portfolio/predictions'), 
                         pattern = "predictions.*\\.csv$", # has "test", followed by 0 or more characters,
                                                            # then ".csv", and then nothing else ($)
                         full.names = TRUE) # include the directory in the result
df <- tibble(Index = NA, index = NA, ret_5w = NA, ord_class = NA, 
             .pred_1 = NA, .pred_2 = NA, .pred_3 = NA, 
             ticker = NA, model = NA, date = NA)
for (i in 1:length(test_files)) { 
  yo <- read_csv(test_files[i]) %>% select(-.pred_class)
  df <- add_row(df, yo)
}

tickers = c("FDX", 'JPM', "AXP", "GILD","SBUX","BBWI","PARA", "MOS", "AA", "CVX", "PYPL", "AMD", "CAT", "HAL")

conform_data <- function(ticker, interval, provider){
  if (interval == "Daily" & provider == "Yahoo"){
    df <- read_csv(paste0(the_path, "/data_stock_ya/", ticker, ".csv"), show_col_types = FALSE) %>% 
      na.omit()
  } else if (interval == "Daily" & provider == "Tiingo"){
    df <- read_csv(paste0(the_path, "/data_stock_ti/", ticker, ".csv"), show_col_types = FALSE) %>% 
      na.omit() %>% 
      rename(index = date, open = adjOpen, high = adjHigh, low = adjLow, close = adjClose, 
             adjusted = adjClose, volume = adjVolume)    
  } else if (interval == "Daily" & provider == "fmpr"){
    df <- read_csv(paste0(the_path, "/data_stock_fmpr/", ticker, ".csv"), show_col_types = FALSE) %>% 
      rename(index = date, adjusted = adjClose)    
  }
  df <- df %>% arrange(index)
  return(df)
}

create_prices_vs_pred <- function(yo) { 
    p1 <- ggplot(yo, aes(x = index, y = adjusted)) + 
      geom_point(aes(col = score)) + 
      annotate("text", x = yo$index[10], y = 1.1 * yo$adjusted[10], label = yo$ticker[1], color = "black") + 
      #scale_color_gradientn(colours = terrain.colors(6)) + 
      scale_color_gradient(low = "red", high = "green") + 
      scale_x_bd(business.dates=yo$index, max.major.breaks = 20, labels=date_format("%d %b '%y"), expand = c(0,0.1)) + 
      #ggtitle(label = tickers[i]) + 
      facet_wrap(~ model, nrow=3) 
    yo <- grid.arrange(p1)
    yo
}

```

```{r}
pdf(paste0("returns_vs_predictions", today(), ".pdf"), width=13, height=8, onefile = TRUE) 
for (i in 1:length(tickers)) { 
  print(tickers[i])
  yo <- df |> filter(ticker == tickers[i]) |>  
    mutate(class_pred = if_else(.pred_3 > .pred_2 & .pred_3 > .pred_1, 3, 
                                if_else(.pred_1 > .pred_2 & .pred_1 > .pred_3, 1, 2))) |> 
    select(-Index) |> arrange(date) |> group_by(index, model) |> slice(1) |> 
    select(index, .pred_1, .pred_2, .pred_3, ticker, model, date) |> 
    mutate(score = case_when(.pred_3 > .pred_2 & .pred_2 > .pred_1 ~ 6, 
                             .pred_2 > .pred_3 & .pred_3 > .pred_1 ~ 5, 
                             .pred_3 > .pred_1 & .pred_1 > .pred_2 ~ 4, 
                             .pred_1 > .pred_3 & .pred_3 > .pred_2 ~ 3, 
                             .pred_2 > .pred_1 & .pred_1 > .pred_3 ~ 2, 
                             TRUE ~ 1)) 
  
  yo_tick <- conform_data(tickers[i], interval = "Daily", provider = "fmpr") |> select(index, adjusted) 
  yo_df <- left_join(yo, yo_tick, by = "index") |> filter(index > "2022-07-28") 
  create_prices_vs_pred(yo_df)
  Sys.sleep(2) 
  }
dev.off()
```



## Do an etf or ticker contain NA or 0? 

```{r eval=FALSE}
check_for_na <- function(ticker) { 
  df <- conform_data(ticker, "Daily", "fmpr") %>% 
    select(index, open, high, low, close, adjusted) %>% 
    summarize_all((~ sum(is.na(.))))
  return(df)
}

check_for_zero <- function(ticker) { 
    df <- conform_data(ticker, "Daily", "fmpr") %>% 
    select(open, high, low, close, adjusted) %>% 
    filter(if_any(everything(.), ~ . == 0))
  }
## checking for 0 or NA
check_na <- tibble(tickers = c("FDX", "SPY", "IYT")) %>% 
  mutate(number_na = map(tickers, check_for_na)) %>% 
  unnest(cols = c(number_na))

check_naa <- tibble(tickers = c("FDX", "SPY", "IYT")) %>% 
  mutate(number_zero = map(tickers, check_for_zero)) 
df <- check_naa %>% unnest()
```



```{r}
library(stringr)
file_n = "/portfolio/predictions/predictions_2022-09-03.csv"
yo <- read_csv(glue(the_path, file_n)) 
yo$model <- str_replace_all(yo$model, "V7.1.e Long", "V71e Long")
yo$model <- str_replace_all(yo$model, "V6.2e Long", "V62e Long")
yo$model <- str_replace_all(yo$model, "Long Long", "Long")
write_csv(yo, glue(the_path, file_n))
  
```

