---
title: "V08 - Exploration of Relative markets"
author: "FdR"
date: "4/29/2022"
output: html_document
---

```{r setup}
knitr::opts_chunk$set(
	echo = FALSE,
	message = FALSE,
	warning = FALSE
)
```
Book to read :-)
https://www.tmwr.org/


TODO: 
1. Sort out the na.omit.... that hides the problem... do we have rows with no data?  rows with 0 values?
2. We don't do small cap (doesn't work with optionns).  
2. TLT vs HYG is this of any values?
3.  percentage in sector below 50SMA? percentage above 200SMA
4.  What is rolling_cor20_ret_etf1 from model 2... do we have this included?
5. Maybe the min and max variables should be included in the dim_roc variables.  Not sure how high they are on the 7 models. 

How a stock do comparing to its sector is more important than how it does comparing to the market. etf2 > etf1 in terms of information. 

```{r basics}
library(dplyr)
library(purrr)
library(readr)
library(stringr)
library(glue)
library(lubridate)
library(roll)
library(tidyr)

the_path <- here::here()

### tickers I will be working on ... 
tickers = c("AMD", "TSM", "QRVO", "AMAT", "BAH", "PYPL", "AXP", "JPM", 
            "GILD", "PKI", "BBWI", "SBUX", "DIS", "PARA",
            "FDX", "CAT", "AA", "CVX", "HAL", "MOS", "STLD") 

etf1 = c("QQQ", "QQQ", "QQQ", "QQQ", "SPY", "QQQ", "SPY", "SPY", 
         "SPY", "SPY", "SPY", "SPY", "SPY", "SPY", 
         "SPY", "SPY", "SPY", "SPY", "SPY", "SPY", "SPY")

etf2 = c("SMH", "SMH", "SMH", "SMH", "HACK", "IPAY", "XLF", "XLF", 
         "XLV", "XLV", "XLY", "XLY", "VOX", "VOX", 
         "IYT", "XLI", "XME", "XLE", "VDE", "VAW", "VAW")

### Function to harmonize the data. 
### ### This is copied from summary_report_v3
conform_data <- function(ticker){
    df <- read_csv(paste0(the_path, "/data_stock_fmpr/", ticker, ".csv"), 
                   show_col_types = FALSE) |>  
      rename(index = date, adjusted = adjClose) |> 
      arrange(index)   
    return(df)
}

get_fmpr_etf_holder <- function(etf) { 
  base_url <- "https://financialmodelingprep.com/api/v3/"
  endpoint <- 'etf-holder/'
  headers = c(`Upgrade-Insecure-Requests` = '1')
  params = list(`datatype` = 'json', 
                `apikey` = "9b274cc7e7560cdb56d931b697c1ed45")
  res <- httr::GET(url = glue(base_url, endpoint, etf), 
                   httr::add_headers(.headers = headers), query = params)
  return_json <- httr::content(res, as = "text")
  d <- jsonlite::fromJSON(return_json) %>% tibble::as_tibble()
  d <- tibble::add_column(d, etf, .before = 1)
  d <- d %>% select(-isin, -cusip, -sharesNumber) %>% arrange(desc(weightPercentage))
  write_csv(d, paste0(the_path, "/analysis/etf/", etf, "_", today(), ".csv"))
  return(d)
}

get_fmpr_prices <- function(ticker, from = "2001-01-02", to = today()) { 
  base_url <- "https://financialmodelingprep.com/api/v3/"
  endpoint <- 'historical-price-full/'
  headers = c(`Upgrade-Insecure-Requests` = '1')
  params = list(`datatype` = 'json', `from` = from, `to` = to, 
                `apikey` = "9b274cc7e7560cdb56d931b697c1ed45")
  res <- httr::GET(url = glue(base_url, endpoint, ticker), 
                   httr::add_headers(.headers = headers), query = params)
  return_json <- httr::content(res, as = "text")
  d <- jsonlite::fromJSON(return_json)
  d <- tibble::as_tibble(d$historical)
  write_csv(d, glue({the_path}, "/data_stock_fmpr/", {ticker}, ".csv"))
}

## function to have percentage in etf above a certain amount.  
create_small_ma_df <- function(ticker) {
  df <- conform_data(ticker, interval = "Daily", provider = "fmpr") %>% 
    filter(is.na(volume) == FALSE) %>% 
    mutate(ema19 = TTR::EMA(adjusted, n = 19), 
           ema37 = TTR::EMA(adjusted, n = 37), 
           sma67 = TTR::SMA(adjusted, n = 67), 
           sma200 = TTR::SMA(adjusted, n = 200), 
           above_ema19 = if_else(adjusted > ema19, 1, 0), 
           above_ema37 = if_else(adjusted > ema37, 1, 0), 
           above_sma67 = if_else(adjusted > sma67, 1, 0), 
           above_sma200 = if_else(adjusted > sma200, 1, 0), 
           volume_sma21 = TTR::SMA(volume, n = 21), 
           volume_above_sma21 = if_else(volume > volume_sma21, 1, 0), 
           roc2 = log(adjusted, lag(adjusted, n = 2)), 
           volat_roc2_23days = roll_sd(roc2, width = 23), 
           volat_roc2_293days = roll_sd(roc2, width = 293), 
           stv_above_ltv = if_else(volat_roc2_23days > volat_roc2_293days, 1, 0)
           ) %>% 
    select(index, above_ema19, above_ema37, above_sma67, above_sma200, volume_above_sma21, 
           stv_above_ltv) 
  return(df)
}

possibly_create_small_ma_df <- possibly(.f = create_small_ma_df, otherwise = NA)

### functions to get etf proportion of ticker above some MA
portion_above_ma <- function(etf){ 
  df_etf <- get_fmpr_etf_holder(etf) %>% 
    select(asset) %>% filter(str_length(asset) <= 4)
  for (i in 1:nrow(df_etf)) { 
    get_fmpr_prices(df_etf$asset[i]) 
    print(paste0("Downloaded ticker ", df_etf$asset[i])) 
  } 
  yo <- df_etf %>% 
    mutate(var_above = map(asset, possibly_create_small_ma_df))
  yo2 <- yo %>% unnest(cols = c(var_above)) %>% 
    group_by(index) %>% 
    summarise(perc_above_19ema = sum(above_ema19, na.rm = TRUE) / n(), 
              perc_above_37ema = sum(above_ema37, na.rm = TRUE) / n(), 
              perc_above_67sma = sum(above_sma67, na.rm = TRUE) / n(), 
              perc_above_sma200 = sum(above_sma200, na.rm = TRUE) / n(), 
              perc_volume_above_sma21 = sum(volume_above_sma21, na.rm = TRUE) / n(), 
              perc_stv_above_ltv = sum(stv_above_ltv, na.rm = TRUE) / n())
  return(yo2)
  }

```

# Building the basic df 

## Ticker df 

```{r base_df}
create_base_fin_df_v8 <- function(df){
  df <- df %>%  
    select(index, open, high, low, close, adjusted, volume) %>% arrange(index) %>% 
    mutate(open = as.numeric(open), high = as.numeric(high), low = as.numeric(low), 
           close = as.numeric(close), adjusted = as.numeric(adjusted), 
           volume = as.numeric(volume)) %>% filter(is.na(volume) == FALSE)

  #for the ADX and atr
  adx <- TTR::ADX(df[,3:5], n = 17) %>% as_tibble() %>% 
    select(dim_adx17 = ADX, meltp_din17 = DIn, dim_dip17 = DIp)          ###YES V2-newish
  df <- bind_cols(df, adx) %>% 
    mutate(meltp_adx_slope5 = dim_adx17 / lag(dim_adx17, 5), 
           dim_dip17_slope5 = dim_dip17 / lag(dim_adx17, 5))
  yo <- TTR::ATR(df[,3:5], n = 13) %>% as_tibble() %>% select(atr13 = atr)    ###YES V2
  df <- bind_cols(df, yo) %>% mutate(dim_atr13 = (atr13 / close)) 
  yo <- TTR::ATR(df[,3:5], n = 19) %>% as_tibble() %>% select(atr19 = atr)    ###YES NEW
  df <- bind_cols(df, yo) %>% mutate(meltp_atr19 = (atr19 / close)) 
  
  # Adding the other variables such a moving averages and relative strength index
  df <- df %>% 
    mutate(roc1 = log(adjusted / lag(adjusted, n = 1)), 
           roc3 = log(adjusted / lag(adjusted, n = 3)), 
           dim_roc3 = log(adjusted / lag(adjusted, n = 3)), 
           roc5 = log(adjusted / lag(adjusted, n = 5)), 
           dim_roc7 = log(adjusted / lag(adjusted, n = 7)), 
           dim_roc11 = log(adjusted / lag(adjusted, n = 11)), 
           dim_roc17 = log(adjusted / lag(adjusted, n = 17)), 
           roc21 = log(adjusted / lag(adjusted, n = 21)), 
           dim_roc31 = log(adjusted / lag(adjusted, n = 31)), 
           dim_roc61 = log(adjusted / lag(adjusted, n = 61)), 
           dim_roc97 = log(adjusted / lag(adjusted, n =97)), 
           dim_roc127 = log(adjusted / lag(adjusted, n =127)), 
           roc126 = log(adjusted / lag(adjusted, n = 126)), 
           dim_roc157 = log(adjusted / lag(adjusted, n = 157)), 
           dim_roc193 = log(adjusted / lag(adjusted, n = 193)), 
           dim_roc223 = log(adjusted / lag(adjusted, n = 223)), 
           ema20 = TTR::EMA(adjusted, 20), 
           ema40 = TTR::EMA(adjusted, 40), 
           sma50 = TTR::SMA(adjusted, 50), 
           sma100 = TTR::SMA(adjusted, 100), 
           sma200 = TTR::SMA(adjusted, 200), 
           
           ema40_slope5 = ema40 / lag(ema40, 5), 
           sma50_perc = log(adjusted / sma50), 
           sma200_perc= log(adjusted / sma200),  
           roll_mean_roc126_126 = roll_mean(roc126, width = 126), 
           roll_mean_roc126_252 = roll_mean(roc126, width = 252), 
           roll_sd_roc126_126 = roll_sd(roc126, width = 126), 
           roll_mean_sma200_1 = roll_mean(sma200_perc, width = 293), 
           roll_sd_sma200_1 = roll_sd(sma200_perc, width = 293), 
           
           std_away_sma200_1 = (sma200_perc - roll_mean_sma200_1) / roll_sd_sma200_1, ###YES V2
           std_away_roc126_126 = (roc126 - roll_mean_roc126_126) / roll_sd_roc126_126,###YES V2Mom    
           corr199_sma50_sma200 = roll_cor(sma50, sma200, width = 199),  ###YES V6
           corr127_ema20_sma50 = roll_cor(ema20, sma50, width = 127),    ###YES
           corr251_ema20_sma50 = roll_cor(ema20, sma50, width = 251),    ###YES V3
           corr63_atr13_atr19 = roll_cor(atr13, atr19, width = 61),      ###YES NEW
           
           roll_sd_sma50_2 = roll_sd(sma50_perc, width = 512), 
           roll_mean_sma50_2 = roll_mean(sma50_perc, width = 252), 
           meltp_diff_sd_sma50_2 = (sma50_perc - roll_mean_sma50_2) / roll_sd_sma50_2,  
           
           
           rsi13 = TTR::RSI(close, 13), 
           rsi19 = TTR::RSI(close, 19), 
           dim_rsi13_slope5 = rsi13 / lag(rsi13, 5), 
           volum_sma47 = TTR::SMA(volume,  n = 47), 
           volum_sma97 = TTR::SMA(volume,  n = 97), 
           volum_sma200 = TTR::SMA(volume,  n = 200), 
           volum200_perc = log(volume / volum_sma200), 
           volum97_perc = log(volume / volum_sma97), 
           
           corr252_rsi19_sma50 = roll_cor(rsi19, sma50, width = 252),   ###YES V3  
           corr127_rsi13_ema40 = roll_cor(rsi13, ema40, width = 127),   ###YES V3-newish 
           volat_volu97_51days = roll_sd(volum200_perc, width = 51),    ###YES V2  
           volat_volu200_21days = roll_sd(volum200_perc, width = 21),   ###YES V2  
           volat_volu200_252days = roll_sd(volum200_perc, width = 252), ###YES V2
           ma_cross_l = sma50 / sma100,                                 ###YES V2
           corr251_volum_sma47_200 = roll_cor(volum_sma47, volum_sma200, width=252), ###YES V3
           
           # percent from high and low
           max_63 = adjusted / roll_max(adjusted, width = 63),          ###YES V2    
           min_63 = adjusted / roll_min(adjusted, width = 63),          ###YES V2 
           min_126 = adjusted / roll_min(adjusted, width = 126),        ###Yes V3
           max_252 = adjusted / roll_max(adjusted, width = 252),        ###YES V2
           min_252 = adjusted / roll_min(adjusted, width = 252),        ###YES V2
           
           # Volatility of returns
           volat_roc1_19days = roll_sd(roc1, width = 19),               ### these 2 var are highly
           volat_roc1_63days = roll_sd(roc1, width=63),                 ### corr.  So new below
           cor_volatroc1_1963days = roll_cor(volat_roc1_19days, volat_roc1_63days, width = 293), 
           volat_roc5_29days = roll_sd(roc5, width = 29),               ###YES V2-Newish
           volat_roc21_252days = roll_sd(roc21, width = 252),           ###YES V2
           
           # forward looking returns                      
           ret_7w = (lead(adjusted, n = 35) / adjusted) - 1)
  
  return(df)
  
}

##########################
## Relative returns df 

relative_returns_v8 <- function(ticker, mkt, sect) { 
  df_ticker <- conform_data(ticker, interval = "Daily", provider = "fmpr") %>% 
    select(index, adjusted) %>% 
    mutate(adjusted_tic = as.numeric(adjusted), 
           roc3_tic = log(adjusted_tic / lag(adjusted_tic, n = 3)), 
           roc5_tic = log(adjusted_tic / lag(adjusted_tic, n = 5)), 
           roc23_tic = log(adjusted_tic / lag(adjusted_tic, n = 23)), 
           volat_roc23_252days = roll_sd(roc23_tic, width = 252)) 
  df_mkt <- conform_data(mkt, interval = "Daily", provider = "fmpr") %>% 
    select(index, adjusted_mkt = adjusted) %>% 
    mutate(roc2_mkt = log(adjusted_mkt / lag(adjusted_mkt, n = 2)),
           roc3_mkt = log(adjusted_mkt / lag(adjusted_mkt, n = 3)),
           roc5_mkt = log(adjusted_mkt / lag(adjusted_mkt, n = 5))) 
  df_sect <- conform_data(sect, interval = "Daily", provider = "fmpr") %>% 
    select(index, adjusted_sect = adjusted) %>% 
    mutate(roc2_sect = log(adjusted_sect / lag(adjusted_sect, n = 2)),
           roc3_sect = log(adjusted_sect / lag(adjusted_sect, n = 3)),
           roc5_sect = log(adjusted_sect / lag(adjusted_sect, n = 5))) 
  
  yo0 <- left_join(df_mkt, df_sect, by = "index") %>% na.omit() %>% 
    mutate(adjusted_ms = adjusted_sect / adjusted_mkt, 
           roc5_ms = log(adjusted_ms / lag(adjusted_ms, 5)), 
           roc11_ms = log(adjusted_ms / lag(adjusted_ms, 11)),
           zzmark_roc23_ms = log(adjusted_ms / lag(adjusted_ms, 23)),   
           zzmark_roc61_ms = log(adjusted_ms / lag(adjusted_ms, 61)),
           zzmark_roc127_ms = log(adjusted_ms / lag(adjusted_ms, 127)),       ###YES
           zzmark_volat251_roc23_ms = roll_sd(zzmark_roc23_ms, width = 252),  ###YES V62
           zzmark_volat251_roc61_ms = roll_sd(zzmark_roc61_ms, width = 251),  ###YES V62
           zzmark_rollcor19_roc2_ms = roll_cor(roc2_mkt, roc2_sect, width=19),###YES
           zzmark_rollcor67_roc5_ms = roll_cor(roc5_mkt, roc5_sect, width=67) ###YES
           ) %>% 
    select(index, zzmark_roc127_ms, zzmark_volat251_roc23_ms, zzmark_volat251_roc61_ms, 
           zzmark_rollcor19_roc2_ms, zzmark_rollcor67_roc5_ms
           )
    
  yo1 <- left_join(df_ticker, df_mkt, by = "index") %>% na.omit() %>% 
    mutate(adj_tm = adjusted_tic / adjusted_mkt, 
           zzmark_roc61_tm = log(adj_tm / lag(adj_tm, 61)),                 
           zzmark_roc127_tm = log(adj_tm / lag(adj_tm, 127)),                 ###YES
           zzmark_volat251_roc61_tm = roll_sd(zzmark_roc61_tm, width = 251),  ###YES V6
           volat251_roc127_tm = roll_sd(zzmark_roc127_tm, width = 251),
           zzmark_rollcor19_roc3_tm = roll_cor(roc3_tic, roc3_mkt, width = 19),###YES
           zzmark_rollcor67_roc5_tm = roll_cor(roc5_tic, roc5_mkt, width = 67),###YES
           rollsd_volatroc_tm = roll_sd(volat_roc23_252days, volat251_roc127_tm, width=252)
           ) %>% 
    select(index, zzmark_roc127_tm, zzmark_volat251_roc61_tm, 
           zzmark_rollcor19_roc3_tm, zzmark_rollcor67_roc5_tm, rollsd_volatroc_tm
           )

  yo2 <- left_join(df_ticker, df_sect, by = "index") %>% na.omit() %>% 
    mutate(adj_ts = adjusted_tic / adjusted_sect, 
           zzmark_roc23_ts = log(adj_ts / lag(adj_ts, 23)),                 
           zzmark_roc61_ts = log(adj_ts / lag(adj_ts, 61)), 
           zzmark_roc127_ts = log(adj_ts / lag(adj_ts, 127)),                ###YES
           zzmark_volat251_roc23_ts = roll_sd(zzmark_roc23_ts, width = 251), ###YES V6
           zzmark_volat251_roc61_ts = roll_sd(zzmark_roc61_ts, width = 251), ###YES V6
           zzmark_rollcor19_roc3_ts = roll_cor(roc3_tic, roc3_sect, width = 19), 
           zzmark_rollcor67_roc5_ts = roll_cor(roc5_tic, roc5_sect, width = 67), 
           rollsd_volatroc_ts = roll_sd(volat_roc23_252days, zzmark_volat251_roc61_ts, width=252)
    ) %>% 
    select(index,  zzmark_roc127_ts, zzmark_volat251_roc23_ts, zzmark_volat251_roc61_ts, 
           zzmark_rollcor19_roc3_ts, zzmark_rollcor67_roc5_ts, rollsd_volatroc_ts
    )
  
  df <- left_join(yo0, yo1) %>% left_join(., yo2)
  
  df_iwd <- conform_data("IWD", interval = "Daily", provider = "fmpr") %>% 
    select(index, adj_iwd = adjusted) 
  df_iwf <- conform_data("IWF", interval = "Daily", provider = "fmpr") %>% 
    select(index, adj_iwf = adjusted)
  df_rus <- left_join(df_iwd, df_iwf) %>% 
    mutate(grow_over_val = adj_iwf / adj_iwd, 
           rus_sma97 = TTR::SMA(grow_over_val, n = 97), 
           rus_sma47 = TTR::SMA(grow_over_val, n = 47), 
           zzmark_ma_cross_rus = rus_sma47 / rus_sma97, 
           zzmark_grow_over_val_roc19 = log(grow_over_val / lag(grow_over_val, 19)), 
           zzmark_grow_over_val_roc67 = log(grow_over_val / lag(grow_over_val, 67)),
           zzmark_grow_over_val_roc127 = log(grow_over_val / lag(grow_over_val, 127))) %>% 
    select(index, zzmark_grow_over_val_roc19, zzmark_grow_over_val_roc67, zzmark_ma_cross_rus, 
           zzmark_grow_over_val_roc127)
  
  df <- left_join(df, df_rus, by = "index")
  
  return(df)
  
}



reduce_df_v8 <- function(old){ 
  df <- old %>% 
    select(Index, 
           ## Version 2
           volat_volu200_252days, volat_roc21_252days, min_252, max_252, ma_cross_l, 
           volat_volu200_21days, std_away_sma200_1, cor_volatroc1_1963days, volat_roc5_29days,  
           max_63, min_63, std_away_roc126_126, 
           ## Version 3
           corr251_ema20_sma50, corr127_ema20_sma50, min_126, 
           corr252_rsi19_sma50, corr127_rsi13_ema40, corr251_volum_sma47_200, 
           
           # Version 6
           corr199_sma50_sma200, volat_volu97_51days, 
           
           ## New
           corr63_atr13_atr19, rollsd_volatroc_ts, rollsd_volatroc_tm, 
           
           ## bring in the etf
           zzmark_volat251_roc61_ms, zzmark_volat251_roc23_ts, zzmark_volat251_roc61_tm, 
           zzmark_volat251_roc23_ms, zzmark_volat251_roc61_ts, 
           zzmark_roc127_ms, zzmark_roc127_tm, zzmark_roc127_ts, 
           zzmark_rollcor19_roc2_ms, zzmark_rollcor67_roc5_ms, 
           zzmark_rollcor19_roc3_tm, zzmark_rollcor67_roc5_tm, 
           zzmark_rollcor19_roc3_ts,  zzmark_rollcor67_roc5_ts, 
           zzmark_grow_over_val_roc19, zzmark_grow_over_val_roc67, zzmark_grow_over_val_roc127, 
           zzmark_ma_cross_rus, 
           
           dim_atr13, dim_adx17, dim_dip17_slope5, dim_rsi13_slope5, 
           dim_roc3, dim_roc7, dim_roc11, dim_roc17, dim_roc31, dim_roc61, dim_roc97, dim_roc127, 
           dim_roc157, dim_roc193, dim_roc223,  
           
           ret_5w
    )
}

```



## picking up the important variables 

```{r}
the_path = here::here()
library(corrr)
library(tidyr)
library(recipes)
library(embed)
library(glue)




analyze_corr_v8 <- function(ticker, mkt, sect) { 
  df0 <- conform_data(ticker, interval="Daily", provider = "fmpr") %>% 
    create_base_fin_df_v8() %>% rename(Index = index)
  df1 <- relative_returns_v8(ticker, mkt, sect) %>% rename(Index = index)
  df2 <- portion_above_ma(sect) %>% rename(Index = index)
  df <- left_join(df0, df1, by = "Index") %>% reduce_df_v8(.) %>% 
    left_join(., df2, by = "Index") %>% 
    mutate(ord_class = as.factor(ntile(ret_5w, 3))) %>% 
    na.omit() 
  recipe_base <- recipe(formula = ord_class ~., data = df) %>% 
    update_role(Index, new_role="ID") %>% 
    step_naomit(columns = all_numeric_predictors()) %>% 
    step_normalize(contains("dim_")) %>% 
    step_normalize(contains("zzmark_")) %>% 
    step_rm("ret_5w") %>% 
    step_pca(contains("dim_"), id = "pca", num_comp=4) %>% 
    step_umap(contains("zzmark_"), prefix = "umap_zzmar", 
              id="umap_zzmar", num_comp = 6, options=list(verbose = TRUE, n_threads = 4)) %>% 
  prep()
  
  yob <- bake(recipe_base, new_data = df)
  df_cor <- yob %>% select(-Index, -ord_class) %>% correlate() %>% shave() 
  yo <- df_cor %>% stretch() %>% mutate(ticker = ticker)
  return(yo %>% drop_na())
}

df_correlation <- tibble(ticker = NA, x = NA, y = NA, r = NA)
  
for (i in 1:length(tickers)) {
  yo <- analyze_corr_v8(tickers[i], etf1[i], etf2[i])
  print(glue("Dealing with ", tickers[i]))
  df_correlation <- bind_rows(df_correlation, yo)
}

yo <- df_correlation %>% group_by(x, y) %>% 
  summarize(median_r = median(r), 
            num_obs = n()) %>% 
  filter(abs(median_r) >= 0.625) %>% arrange(desc(median_r))
```


volat_roc1_19days and volat_roc1_63days and volat_roc5_29days are all highly correlated. So, I will keep volat_roc5_29days and then use the correlation of volat_roc1_19days and volat_roc1_63days.  DONE


# Summary of important variables and correlation (5 weeks)

                          V2    V3    V6    V7       Corr
volat_volu200_252days     1            1             X
volat_roc21_252days       2            4    2        X
min_252                   3                          min_126
ma_cross_l                4            11            X
std_away_sma200_1         5     9                    X
volat_volu200_21days      7                          X
atr14 (melt_atr13)        8                          volat_roc1_19days, volat_roc5_29days, +1
max_252                   9                          max_63
adx_14 (melt_adx17)       10                     
volat_roc1_19days         11                         volat_roc1_63days, volat_roc5_29days
volat_roc5_29days         12                         volat_roc1_63days
min_63 (meltp_min_63)           13                   min_126              
max_63                    17                      
std_away_roc126_126       3*                   
corr251_ema20_sma50             1      3    4              
volat_roc1_63days               2      10   7        volat_roc1_19days / volat_roc5_29days
corr127_ema20_sma50             3      13                   
corr251_volum_sma47_200         4
atr19 (cor63_atr13_atr19)       5
corr252_rsi19_sma50             6                    corr126_rsi13_ema40
corr126_rsi13_ema40             8                    corr252_rsi19_sma50
corr199_sma50_sma200                   2

zzmark_volat251_roc61_ms               5
zzmark_volat251_roc23_ts               6
zzmark_volat251_roc61_tm               7
zzmark_volat251_roc23_ms               8

NEW
corr63_atr13_atr19, 







# Missing values 

## Checking on missing values or Zero values 

Checking for missing values and dealing with them. 
```{r mis_val, eval=FALSE}
check_for_na <- function(ticker) { 
  df <- conform_data(ticker, "Daily", "fmpr") %>% 
    select(index, open, high, low, close, adjusted, volume) %>% 
    summarize_all((~ sum(is.na(.))))
  return(df)
}

check_for_zero <- function(ticker) { 
    df <- conform_data(ticker, "Daily", "fmpr") %>% 
    select(open, high, low, close, adjusted, volume) %>% 
    filter(if_any(everything(.), ~ . == 0))
  }

## checking for 0 or NA
check_na <- tibble(tickers = c(tickers, etf1, etf2)) %>% 
  mutate(number_na = map(tickers, check_for_na)) %>% 
  unnest(cols = c(number_na))

check_naa <- tibble(tickers = c(tickers, etf1, etf2)) %>% 
  mutate(number_zero = map(tickers, check_for_zero)) 
df <- check_naa %>% unnest()
```


## fixing NA values 

NA values seems to appear mainly in the Volume part of the data. 
Noticing missing values in GILD, VOX and VAW.  You can have several days in a row with NA in volume.  

Solution: 
We are not touching the volume of the ETF.  So we are only interested in the volume of the stock. 
Noticing that when volume is NA, it is because they were no trading.  So we can just remove these days. 
```{r eval=FALSE}
the_path = here::here()
yo <- read_csv(paste0(the_path, "/data_stock_fmpr/GILD.csv"))
yo_na <- yo %>% filter(is.na(volume))
yo_no_na <- yo %>% filter(is.na(volume) == FALSE)

create_base_fin_df_v8 <- function(df){
  df <- df %>%  
    select(index, open, high, low, close, adjusted, volume) %>% arrange(index) %>% 
    mutate(open = as.numeric(open), high = as.numeric(high), low = as.numeric(low), 
           close = as.numeric(close), adjusted = as.numeric(adjusted), 
           volume = as.numeric(volume)) %>% filter(is.na(volume) == FALSE)
  
}
```



